---
title: "My favorite Places"
author: "Jesica Scott"
date: "April 7, 2019"
output:
  html_document: default
  pdf_document: default
---

## R Markdown

Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

Review criteria
The rubric contains the following two questions:

Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?
Does the web page feature an interactive map that appears to have been created with Leaflet?

## Approach

I will proceed by creating a map consisting of several of my favorite places, enjoy!

## First 

We must call the correct package and tiles.
```{r,echo=TRUE}
library(leaflet)
```

```{r,echo=TRUE}
my_map<-leaflet()%>%addTiles()
```
And here's our first point.
```{r,echo=TRUE}
my_map<-my_map%>%addMarkers(lat=28.0011295,lng=-82.4584515,popup="The Street")
```
The rest follow...
```{r,echo=TRUE}
my_map<-my_map%>%addMarkers(lat=28.0052262,lng=-82.4593097,popup="Jug and Bottle")
my_map<-my_map%>%addMarkers(lat=28.0112232,lng=-82.4587471,popup="Firetruck Park")
my_map<-my_map%>%addMarkers(lat=27.9943182,lng=-82.4595965,popup="Spaddy's Coffee")
my_map<-my_map%>%addMarkers(lat=28.0000022,lng=-82.4556860,popup="Log Park")

my_map
```
And there you have it, done!
